Speeding up eQTL scans in the BXD population using GPU

### 2019-10-08 paper.tex
added some reference in introduction

%Why GPU?
Processing large data set has been a challenge for genome scan. 
We were blessed with Moore's Law for decades, but the Central Processing Unit (CPU) is reaching to its physical limit of transistors. 
Graphics Processing Unit (GPU), originally used as an image processing component of a computer, has shown some compelling results of accelerating computation in various fields.
General Purpose computing Graphics Processor (GPGPU) became popular in the early 2000s because of its ability to natively handel matrix and vector operations. 
Such power is very attractive to the scientific computing community. 
Zhang et al. \citep{zhang2015mixed} used GPU to simultaneously dissect various genetic effects with mixed linear model.

>>>>

%Why GPU?
Processing large data set has been a challenge for genome scan. 
We were blessed with Moore's Law for decades, but the Central Processing Unit (CPU) is reaching to its physical limit of transistors. 
Graphics Processing Unit (GPU), originally used as an image processing component of a computer, has shown some compelling results of accelerating computation in various fields.
General Purpose computing Graphics Processor (GPGPU) became popular in the early 2000s because of its ability to natively handel matrix and vector operations. 
Such power is very attractive to the scientific computing community. 
Zhang et al. \citep{zhang2015mixed} used GPU to simultaneously dissect various genetic effects with mixed linear model. 
Chapuis et all. \citep{chapuis2013graphics} utilizes GPU to offset heavy computation to deploy various ways for a more pricise detection of QTLs threashold. 
By using GPU-backed machine learning libraries like TensorFlow, Taylor-Weiner et al. \citep{taylor2019scaling} reimplemented QTL mapping  and Bayesian non-negative matrix factorization, achieving greater than 200 times speedup compared to CPU-based versions. 
The ease of using such library will push method-development for genomeic research.
